---
title       : 1920's cars breaking distance vs. speed
subtitle    : A Shiny app
author      : Felipe Godoi Rosario
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## 2. General idea

- The general idea of the Shiny application is to predict the breaking distance for a hypothetical 1920's car based on its speed.
- The dataset used is called "cars" and it's a R default package.
- The data give the speed of cars and the distances taken to stop. The data were recorded in the 1920s, so that's why our model is for a 1920's car. :-)

--- .class #id 

## 3. The dataset

Here's a summary of the dataset. It has 50 observations on 2 variables.

```{r}
data(cars)
dim(cars)
summary(cars)
```

--- .class #id 

## 4. Plotting the observations

In the Shiny app there's this plot of the observations.

```{r}
plot(cars, xlab = "Speed (mph)", ylab = "Stopping distance (ft)", las = 1, xlim = c(0, 25))
```

--- .class #id 

## 5. Linear Model and predicting

I created a Linear Model based on the data:

```{r, results='hide'}
fm <- lm(dist ~ speed, data = cars)
```

Using it it's simple to predict a breaking distance giving the speed (23 mph, for example):

```{r}
predict(fm, data.frame(speed = 23))
```

According to our model a car at 23 mph would take 72.87 feet to stop.

A very basic machine learning!

Thank you!

